\textbf{COMP0085 Summative Assignment}

### 2022-12-30 submission.tex
add loopy bp and refactor ep models

@@

\[\eta_{i, \neg s_j} =  \log \left(\frac{\lambda_i}{1-\lambda_i}\right) + \sum_{k\in ne(j), k\neq j}^{K} \log\left(\frac{\theta_{kj}}{1-\theta_{kj}} \right)\]

Knowing $\log \left(\frac{\lambda_i}{1-\lambda_i} \right)s_i = b_i s_i$ and $\xi_{kj} = \log\left(\frac{\theta_{kj}}{1-\theta_{kj}} \right)$:

\[\eta_{i, \neg s_j} =  b_i + \sum_{k\in ne(j), k\neq j}^{K} \xi_{kj}\]

@@

\[\eta_{j, \neg s_i} =  b_j + \sum_{k\in ne(i), k\neq i}^{K} \xi_{ki}\]

@@

\[\xi_{ij} = \log \left( \frac{1+\exp\left( W_{ij}  + \eta_{j, \neg s_i}\right)}{1+\exp\left( \eta_{i, \neg s_j}\right)} \right)\]

@@

>>>>

\newpage
The Python code for the binary latent factor model:
\lstinputlisting[language=Python]{src/models/binary_latent_factor_model.py}

@@

\[\eta_{i, \neg s_j} =  \log \left(\frac{\lambda_i}{1-\lambda_i}\right) + \sum_{k\in ne(i), k\neq j}^{K} \log\left(\frac{\theta_{ki}}{1-\theta_{ki}} \right)\]

Knowing $b_i=\log \left(\frac{\lambda_i}{1-\lambda_i}\right)$ and $\xi_{ki}=\log\left(\frac{\theta_{ki}}{1-\theta_{ki}} \right)$:

\[\eta_{i, \neg s_j} =  b_i + \sum_{k\in ne(i), k\neq j}^{K} \xi_{ki}\]

@@

\[\eta_{j, \neg s_i} =  b_j + \sum_{k\in ne(j), k\neq i}^{K} \xi_{kj}\]

@@

\[\xi_{ij} = \log \left( \frac{1+\exp\left( W_{ij}  + \eta_{i, \neg s_j}\right)}{1+\exp\left( \eta_{i, \neg s_j}\right)} \right)\]

@@

\newpage
\section{Question 6}

\begin{figure}[h]
\centering
\includegraphics[scale=0.4]{outputs/q6/all-latent-factors}
\caption{Latent factors learned with EP/Loopy-BP}
\label{fig:6-latent-factors}
\end{figure}

\newpage
The Python code for the Boltzmann machine:
\lstinputlisting[language=Python]{src/models/boltzmann_machine.py}

\newpage
The Python code for message passing:
\lstinputlisting[language=Python]{src/models/message_passing.py}

\newpage
The rest of the Python code for question 6:
\lstinputlisting[language=Python]{src/solutions/q6.py}
